Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
Experiments

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
\label{sec:uci}
%
We consider 8 UCI~\cite{UCI} benchmarks, consisting of a range of binary and multi-class classification tasks with varying data set sizes. We first train two-layer MLPs for each of the classification tasks and follow the setup in \cref{sec:methods} for \our. That is, after training we construct the \our dual and use the resulting model for uncertainty quantification. For comparison, we used the same hyperparameters for the neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly perform hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits.
 %Depending on task dimension and complexity, our model can match the neural network MAP in negative log-predictive density (NLPD) even with a low number of inducing points (see \cref{tbl:uci} left).
In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD). We match the predictive performance despite being sparse (here, $M=256$). Results for $M=16,32,64,128,256$ are included in \cref{app:uci} with full experiment details.

In \cref{tbl:uci} (right), we also include an ablation and comparison (to \cite{immer2021improving}) study with a fixed low number of inducing points ($M=32$). The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points. This is even more apparent from \cref{fig:uci} which shows the benefits of \our in summarizing the full data distribution onto a small set of inducing points over just picking a random subset.

@@

    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
    % \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    % \toprule
    % & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
    % \midrule
    % \multirow{2}{*}{FMNIST}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \midrule
    % \multirow{2}{*}{CIFAR-10}
    % & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    % \bottomrule
    % \end{tabular}
  \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    \toprule
    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$   \\
    \midrule
    \multirow{2}{*}{MNIST}
    & MAP & \val{98.22}{0.13} & \val{0.061}{0.004} & \val{0.006}{0.001} \\
    & BNN predictive \cite{todo} & \val{93.03}{0.13} & \val{0.369}{0.003} & \val{0.168}{0.001} \\
    & GLM predictive & \val{98.40}{0.05} & \val{0.054}{0.002} & \val{0.007}{0.001} \\
    & GP predictive $m=3200$ & \val{98.22}{0.13} & \val{0.058}{0.001} & \val{0.003}{0.000} \\
    & GP predictive NN $m=1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001} \\
    & GP predictive $m=1024$  &  \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022} \\
    & \our NN $m=1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001} \\
    & \our $m=1024$ &  \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001} \\
    \midrule
    \multirow{2}{*}{FMNIST}
    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    & BNN predictive & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    & BNN predictive (Ritter et al.) & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    & GLM predictive & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    & GP predictive $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
    & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
    & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
    & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
    & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
    \bottomrule
  \end{tabular}

% & \sc \sc gp predictive  &  \val{76.28333}{1.849} & \val{0.70168}{0.02883} & \val{0.07049}{0.02154} \\
% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{97.70333}{0.074} & \val{0.08027}{0.00248} & \val{0.01052}{0.00097} \\
% & \sc \our &  \val{98.06667}{0.060} & \val{0.06312}{0.00284} & \val{0.00493}{0.00086} \\
% & \sc \our NN &  \val{98.02000}{0.122} & \val{0.06583}{0.00294} & \val{0.00714}{0.00096} \\
% M=512
% & \sc \our &  \val{96.05}{0.00} & \val{0.85}{0.01} & \val{0.50}{0.00} \\
% & \sc \sc gp predictive  &  \val{14.79}{0.01} & \val{2.30}{0.02} & \val{0.02}{0.01} \\
% & \sc \sc gp predictive NN \cite{immer2021improving} &  \val{91.49}{0.01} & \val{1.25}{0.01} & \val{0.61}{0.00} \\
% & \sc \our NN &  \val{96.96}{0.00} & \val{0.63}{0.00} & \val{0.40}{0.00} \\

% M=1024

>>>>

\subsection{Capturing uncertainty in UCI tasks under supervised learning}
\label{sec:uci}
%
We consider eight UCI benchmarks~\cite{UCI}, covering of a variety of binary and multi-class classification tasks with different data set sizes. We initially train a two-layer MLP for each of the classification tasks and follow the setup in \cref{sec:methods} for \our. That is, after training we construct the \our dual and use the resulting model for uncertainty quantification. For comparison, we used the same hyperparameters for the neural network training as in the UCI experiments of \cite{immer2021improving}, and similarly perform hyperparameter search over the prior precision $\delta$, and run the experiment over $10$ random splits. In \cref{tbl:uci} (left), we compare our model to the NN MAP estimate, mean-field VI, a Bayesian NN, and a GLM model (see \cite{immer2021improving} for the baselines) in negative log-predictive density (NLPD). We match the predictive performance despite being sparse (here, $M=256$). Results for $M=16,32,64,128,256$ are included in \cref{app:uci} with full experiment details.

In \cref{tbl:uci} (right), we also include an ablation and comparison study (to \cite{immer2021improving}) with a fixed low number of inducing points ($M=32$). The comparison shows that our sparse method is able to summarize the information of the full data set more efficiently than sparse subset methods, and can match the performance of the full GP even with a low number of inducing points. This is even more apparent from \cref{fig:uci} which shows the benefits of \our in summarizing the full data distribution onto a small set of inducing points over just picking a random subset.

@@

    % THE TABLE CAN BE FORMATTED MORE LIKE THIS
    \begin{tabular}{l l C{\tblw} C{\tblw} C{\tblw} C{\tblw}}
    \toprule
    & Method & ACC~$\uparrow$ & NLPD~$\downarrow$ & ECE~$\downarrow$ & OOD-AUC~$\uparrow$  \\
    \midrule
    \multirow{2}{*}{FMNIST} 
    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
    \midrule
    \multirow{2}{*}{CIFAR-10} 
    & MAP & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & BNN predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & BNN predictive \cite{todo} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & GLM predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & GP predictive & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & \our (NN) & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\
    & \our & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} & \val{0.000}{0.000} \\    
    \bottomrule
    \end{tabular}
